rbcL ASV clustering

### 2019-11-02 code/rbcl_asv_clustering.Rmd
renamed OTUs

# name each OTU, lettered in order of rel abund
otu_names <- tibble(otu = as.character(1:9), 
                    otu_name = c("Chloromonas spp. C",
                                 "Sanguina B",
                                 "Chlainomonas A",
                                 "Chloromonas muramotoi D",
                                 "Chloromonas E",
                                 "Chloromonas G",
                                 "Algae F",
                                 "Trebouxiophyceae H",
                                 "Chloromonas krienitzii"))

>>>>

# name each OTU, lettered in order of rel abund
otu_names <- tibble(otu = as.character(1:9), 
                    otu_name = c("Other Chloromonas",
                                 "Sanguina B",
                                 "Chlainomonas A",
                                 "Chloromonas muramotoi C",
                                 "Chloromonas D",
                                 "Chloromonas F",
                                 "Algae E",
                                 "Trebouxiophyceae G",
                                 "Chloromonas krienitzii"))
